Expert pianists make specific exaggerations for teaching

### 2022-09-02 paper/manuscript.tex
finalise the manuscript
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{teaching, skill transmission, sensorimotor communication, artistic expression, music}
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The sound of teaching music: Expert pianists' performance modulations for novices},
  pdfauthor={Atsuko Tominaga1,*, Günther Knoblich1, \& Natalie Sebanz1},
  pdflang={en-EN},
  pdfkeywords={teaching, skill transmission, sensorimotor communication, artistic expression, music},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{The sound of teaching music: Expert pianists' performance modulations for novices}
\author{Atsuko Tominaga\textsuperscript{1,*}, Günther Knoblich\textsuperscript{1}, \& Natalie Sebanz\textsuperscript{1}}
\date{}

\shorttitle{The sound of teaching music}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-art-teaching-1-1} \caption{\label{fig:art-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KOT (ms) when playing the piece with articulation. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-art-teaching-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-teaching-1-1} \caption{\label{fig:dyn-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KV (0-127) when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-teaching-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-diff-teaching-1-1} \caption{\label{fig:dyn-diff-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KV Difference at transition points when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-diff-teaching-1}
\end{figure}

@@

\begin{tabular}{lllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Teaching} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Articulation & Yes & 10 & 181.27 & 10.99 & 3.47\\
Teaching & Articulation & Yes & 10 & 184.72 & 13.02 & 4.12\\
Performing & Articulation & No & 21 & 193.49 & 18.75 & 4.09\\
Teaching & Articulation & No & 21 & 196.67 & 20.52 & 4.48\\
Performing & Dynamics & Yes & 10 & 182.43 & 11.52 & 3.64\\
Teaching & Dynamics & Yes & 10 & 187.15 & 11.73 & 3.71\\
Performing & Dynamics & No & 21 & 191.48 & 18.56 & 4.05\\
Teaching & Dynamics & No & 21 & 193.50 & 21.22 & 4.63\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.1 B) or dynamics (Fig.1 C). Teaching indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{Teaching} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Articulation & Legato & Yes & 10 & 21.57 & 16.18 & 5.12\\
Performing & Articulation & Staccato & Yes & 10 & -119.66 & 22.84 & 7.22\\
Teaching & Articulation & Legato & Yes & 10 & 25.43 & 13.11 & 4.15\\
Teaching & Articulation & Staccato & Yes & 10 & -127.39 & 15.95 & 5.04\\
Performing & Articulation & Legato & No & 21 & 10.40 & 16.57 & 3.62\\
Performing & Articulation & Staccato & No & 21 & -132.48 & 19.03 & 4.15\\
Teaching & Articulation & Legato & No & 21 & 11.36 & 14.71 & 3.21\\
Teaching & Articulation & Staccato & No & 21 & -136.84 & 21.52 & 4.70\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.1 B) or dynamics (Fig.1 C). Teaching indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{Teaching} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Dynamics & Forte & Yes & 10 & 85.20 & 7.76 & 2.45\\
Performing & Dynamics & Piano & Yes & 10 & 60.27 & 4.57 & 1.44\\
Teaching & Dynamics & Forte & Yes & 10 & 86.96 & 8.76 & 2.77\\
Teaching & Dynamics & Piano & Yes & 10 & 60.11 & 5.93 & 1.87\\
Performing & Dynamics & Forte & No & 21 & 79.97 & 6.82 & 1.49\\
Performing & Dynamics & Piano & No & 21 & 61.33 & 4.40 & 0.96\\
Teaching & Dynamics & Forte & No & 21 & 80.80 & 7.49 & 1.63\\
Teaching & Dynamics & Piano & No & 21 & 60.88 & 4.76 & 1.04\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.1 B) or dynamics (Fig.1 C). Teaching indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{Teaching} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Dynamics & FtoP & Yes & 10 & -14.63 & 5.79 & 1.83\\
Performing & Dynamics & PtoF & Yes & 10 & 24.32 & 9.96 & 3.15\\
Teaching & Dynamics & FtoP & Yes & 10 & -18.81 & 7.26 & 2.30\\
Teaching & Dynamics & PtoF & Yes & 10 & 29.07 & 8.78 & 2.78\\
Performing & Dynamics & FtoP & No & 21 & -10.30 & 5.69 & 1.24\\
Performing & Dynamics & PtoF & No & 21 & 19.23 & 7.71 & 1.68\\
Teaching & Dynamics & FtoP & No & 21 & -11.87 & 6.09 & 1.33\\
Teaching & Dynamics & PtoF & No & 21 & 21.98 & 9.56 & 2.09\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.1 B) or dynamics (Fig.1 C). Teaching indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-art-teaching-2-1} \caption{\label{fig:art-teaching-2}Experiment 2:  Comparison between those with and without piano teaching experience in terms of KOR when playing the piece with articulation. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-art-teaching-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-teaching-2-1} \caption{\label{fig:dyn-teaching-2}Experiment 2: Comparison between those with and without piano teaching experience in terms of KV (0-127) when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-teaching-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-diff-teaching-2-1} \caption{\label{fig:dyn-diff-teaching-2}Experiment 2: Comparison between those with and without piano teaching experience in terms of KV Difference at transition points when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-diff-teaching-2}
\end{figure}

@@

\begin{tabular}{lllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Teaching} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Articulation & Yes & 11 & 0.954 & 0.046 & 0.014\\
Teaching & Articulation & Yes & 11 & 0.964 & 0.049 & 0.015\\
Performing & Articulation & No & 9 & 0.951 & 0.035 & 0.012\\
Teaching & Articulation & No & 9 & 0.967 & 0.052 & 0.017\\
Performing & Dynamics & Yes & 11 & 0.953 & 0.046 & 0.014\\
Teaching & Dynamics & Yes & 11 & 0.958 & 0.047 & 0.014\\
Performing & Dynamics & No & 9 & 0.958 & 0.041 & 0.014\\
Teaching & Dynamics & No & 9 & 0.955 & 0.052 & 0.017\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.5 B) or dynamics (Fig.5 C). Teaching indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{Teaching} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Articulation & Legato & Yes & 11 & 0.115 & 0.074 & 0.022\\
Performing & Articulation & Staccato & Yes & 11 & -0.755 & 0.034 & 0.010\\
Teaching & Articulation & Legato & Yes & 11 & 0.122 & 0.064 & 0.019\\
Teaching & Articulation & Staccato & Yes & 11 & -0.776 & 0.034 & 0.010\\
Performing & Articulation & Legato & No & 9 & 0.120 & 0.071 & 0.024\\
Performing & Articulation & Staccato & No & 9 & -0.728 & 0.050 & 0.017\\
Teaching & Articulation & Legato & No & 9 & 0.120 & 0.081 & 0.027\\
Teaching & Articulation & Staccato & No & 9 & -0.749 & 0.073 & 0.024\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.5 B) or dynamics (Fig.5 C). Teaching indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{Teaching} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Dynamics & Forte & Yes & 11 & 81.06 & 6.52 & 1.97\\
Performing & Dynamics & Piano & Yes & 11 & 62.49 & 5.55 & 1.67\\
Teaching & Dynamics & Forte & Yes & 11 & 83.32 & 6.48 & 1.95\\
Teaching & Dynamics & Piano & Yes & 11 & 59.50 & 3.59 & 1.08\\
Performing & Dynamics & Forte & No & 9 & 82.02 & 10.15 & 3.38\\
Performing & Dynamics & Piano & No & 9 & 62.36 & 4.11 & 1.37\\
Teaching & Dynamics & Forte & No & 9 & 83.06 & 11.54 & 3.85\\
Teaching & Dynamics & Piano & No & 9 & 61.81 & 3.76 & 1.25\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.5 B) or dynamics (Fig.5 C). Teaching indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{Teaching} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Dynamics & FtoP & Yes & 11 & -14.43 & 6.20 & 1.87\\
Performing & Dynamics & PtoF & Yes & 11 & 14.96 & 6.78 & 2.04\\
Teaching & Dynamics & FtoP & Yes & 11 & -19.27 & 4.33 & 1.30\\
Teaching & Dynamics & PtoF & Yes & 11 & 20.77 & 5.71 & 1.72\\
Performing & Dynamics & FtoP & No & 9 & -13.64 & 9.46 & 3.15\\
Performing & Dynamics & PtoF & No & 9 & 17.44 & 8.11 & 2.70\\
Teaching & Dynamics & FtoP & No & 9 & -14.84 & 11.08 & 3.69\\
Teaching & Dynamics & PtoF & No & 9 & 20.66 & 12.09 & 4.03\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.5 B) or dynamics (Fig.5 C). Teaching indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

A two-way repeated-measures ANOVA with the factors Condition (teaching vs.~performing) and Transition Type (FtoP vs.~PtoF) showed that there was a significant main effect of Transition Type (\emph{F}(1,19) = 42, \emph{p} \textless{} 0.001, \(\eta_G^2\) = 0.63). However, there was no significant interaction between Condition and Transition Type (\emph{F}(1,19) = 1.10, \emph{p} = 0.306, \(\eta_G^2\) = 0.008, \emph{Fig \ref{fig:vel-diff-2}}).

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{teaching, skill transmission, sensorimotor communication, artistic expression, music}
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Expert pianists make specific exaggerations for teaching},
  pdfauthor={Atsuko Tominaga1,*, Günther Knoblich1, \& Natalie Sebanz1},
  pdflang={en-EN},
  pdfkeywords={teaching, skill transmission, sensorimotor communication, artistic expression, music},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Expert pianists make specific exaggerations for teaching}
\author{Atsuko Tominaga\textsuperscript{1,*}, Günther Knoblich\textsuperscript{1}, \& Natalie Sebanz\textsuperscript{1}}
\date{}

\shorttitle{Expert pianists make specific exaggerations for teaching}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-art-teaching-1-1} \caption{\label{fig:art-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KOT (ms) when playing the piece with articulation (left: legato, right: staccato). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-art-teaching-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-teaching-1-1} \caption{\label{fig:dyn-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KV (0-127) when playing the piece with dynamics (left: forte, right: piano). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-teaching-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-diff-teaching-1-1} \caption{\label{fig:dyn-diff-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KV Difference at transition points when playing the piece with dynamics  (left: forte to piano, right: piano to forte). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-diff-teaching-1}
\end{figure}

@@

\begin{tabular}{lllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{TeachingExp} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Articulation & Yes & 10 & 181.27 & 10.99 & 3.47\\
Teaching & Articulation & Yes & 10 & 184.72 & 13.02 & 4.12\\
Performing & Articulation & No & 21 & 193.49 & 18.75 & 4.09\\
Teaching & Articulation & No & 21 & 196.67 & 20.52 & 4.48\\
Performing & Dynamics & Yes & 10 & 182.43 & 11.52 & 3.64\\
Teaching & Dynamics & Yes & 10 & 187.15 & 11.73 & 3.71\\
Performing & Dynamics & No & 21 & 191.48 & 18.56 & 4.05\\
Teaching & Dynamics & No & 21 & 193.50 & 21.22 & 4.63\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.1 B) or dynamics (Fig.1 C). TeachingExp indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{TeachingExp} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Articulation & Legato & Yes & 10 & 21.57 & 16.18 & 5.12\\
Teaching & Articulation & Legato & Yes & 10 & 25.43 & 13.11 & 4.15\\
Performing & Articulation & Staccato & Yes & 10 & -119.66 & 22.84 & 7.22\\
Teaching & Articulation & Staccato & Yes & 10 & -127.39 & 15.95 & 5.04\\
Performing & Articulation & Legato & No & 21 & 10.40 & 16.57 & 3.62\\
Teaching & Articulation & Legato & No & 21 & 11.36 & 14.71 & 3.21\\
Performing & Articulation & Staccato & No & 21 & -132.48 & 19.03 & 4.15\\
Teaching & Articulation & Staccato & No & 21 & -136.84 & 21.52 & 4.70\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.1 B) or dynamics (Fig.1 C). TeachingExp indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{TeachingExp} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Dynamics & Forte & Yes & 10 & 85.20 & 7.76 & 2.45\\
Teaching & Dynamics & Forte & Yes & 10 & 86.96 & 8.76 & 2.77\\
Performing & Dynamics & Piano & Yes & 10 & 60.27 & 4.57 & 1.44\\
Teaching & Dynamics & Piano & Yes & 10 & 60.11 & 5.93 & 1.87\\
Performing & Dynamics & Forte & No & 21 & 79.97 & 6.82 & 1.49\\
Teaching & Dynamics & Forte & No & 21 & 80.80 & 7.49 & 1.63\\
Performing & Dynamics & Piano & No & 21 & 61.33 & 4.40 & 0.96\\
Teaching & Dynamics & Piano & No & 21 & 60.88 & 4.76 & 1.04\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.1 B) or dynamics (Fig.1 C). TeachingExp indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{TeachingExp} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Dynamics & FtoP & Yes & 10 & -14.63 & 5.79 & 1.83\\
Teaching & Dynamics & FtoP & Yes & 10 & -18.81 & 7.26 & 2.30\\
Performing & Dynamics & PtoF & Yes & 10 & 24.32 & 9.96 & 3.15\\
Teaching & Dynamics & PtoF & Yes & 10 & 29.07 & 8.78 & 2.78\\
Performing & Dynamics & FtoP & No & 21 & -10.30 & 5.69 & 1.24\\
Teaching & Dynamics & FtoP & No & 21 & -11.87 & 6.09 & 1.33\\
Performing & Dynamics & PtoF & No & 21 & 19.23 & 7.71 & 1.68\\
Teaching & Dynamics & PtoF & No & 21 & 21.98 & 9.56 & 2.09\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.1 B) or dynamics (Fig.1 C). TeachingExp indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-art-teaching-2-1} \caption{\label{fig:art-teaching-2}Experiment 2:  Comparison between those with and without piano teaching experience in terms of KOR when playing the piece with articulation (left: legato, right: staccato). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-art-teaching-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-teaching-2-1} \caption{\label{fig:dyn-teaching-2}Experiment 2: Comparison between those with and without piano teaching experience in terms of KV (0-127) when playing the piece with dynamics  (left: forte, right: piano). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-teaching-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-diff-teaching-2-1} \caption{\label{fig:dyn-diff-teaching-2}Experiment 2: Comparison between those with and without piano teaching experience in terms of KV Difference at transition points when playing the piece with dynamics (left: forte to piano, right: piano to forte). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-diff-teaching-2}
\end{figure}

@@

\begin{tabular}{lllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{TeachingExp} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Articulation & Yes & 11 & 0.954 & 0.046 & 0.014\\
Teaching & Articulation & Yes & 11 & 0.964 & 0.049 & 0.015\\
Performing & Articulation & No & 9 & 0.951 & 0.035 & 0.012\\
Teaching & Articulation & No & 9 & 0.967 & 0.052 & 0.017\\
Performing & Dynamics & Yes & 11 & 0.953 & 0.046 & 0.014\\
Teaching & Dynamics & Yes & 11 & 0.958 & 0.047 & 0.014\\
Performing & Dynamics & No & 9 & 0.958 & 0.041 & 0.014\\
Teaching & Dynamics & No & 9 & 0.955 & 0.052 & 0.017\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.5 B) or dynamics (Fig.5 C). TeachingExp indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{TeachingExp} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Articulation & Legato & Yes & 11 & 0.115 & 0.074 & 0.022\\
Teaching & Articulation & Legato & Yes & 11 & 0.122 & 0.064 & 0.019\\
Performing & Articulation & Staccato & Yes & 11 & -0.755 & 0.034 & 0.010\\
Teaching & Articulation & Staccato & Yes & 11 & -0.776 & 0.034 & 0.010\\
Performing & Articulation & Legato & No & 9 & 0.120 & 0.071 & 0.024\\
Teaching & Articulation & Legato & No & 9 & 0.120 & 0.081 & 0.027\\
Performing & Articulation & Staccato & No & 9 & -0.728 & 0.050 & 0.017\\
Teaching & Articulation & Staccato & No & 9 & -0.749 & 0.073 & 0.024\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.5 B) or dynamics (Fig.5 C). TeachingExp indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{TeachingExp} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Dynamics & Forte & Yes & 11 & 81.06 & 6.52 & 1.97\\
Teaching & Dynamics & Forte & Yes & 11 & 83.32 & 6.48 & 1.95\\
Performing & Dynamics & Piano & Yes & 11 & 62.49 & 5.55 & 1.67\\
Teaching & Dynamics & Piano & Yes & 11 & 59.50 & 3.59 & 1.08\\
Performing & Dynamics & Forte & No & 9 & 82.02 & 10.15 & 3.38\\
Teaching & Dynamics & Forte & No & 9 & 83.06 & 11.54 & 3.85\\
Performing & Dynamics & Piano & No & 9 & 62.36 & 4.11 & 1.37\\
Teaching & Dynamics & Piano & No & 9 & 61.81 & 3.76 & 1.25\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.5 B) or dynamics (Fig.5 C). TeachingExp indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

\begin{tabular}{llllllll}
\toprule
Condition & \multicolumn{1}{c}{Technique} & \multicolumn{1}{c}{Subcomponent} & \multicolumn{1}{c}{TeachingExp} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{SEM}\\
\midrule
Performing & Dynamics & FtoP & Yes & 11 & -14.43 & 6.20 & 1.87\\
Teaching & Dynamics & FtoP & Yes & 11 & -19.27 & 4.33 & 1.30\\
Performing & Dynamics & PtoF & Yes & 11 & 14.96 & 6.78 & 2.04\\
Teaching & Dynamics & PtoF & Yes & 11 & 20.77 & 5.71 & 1.72\\
Performing & Dynamics & FtoP & No & 9 & -13.64 & 9.46 & 3.15\\
Teaching & Dynamics & FtoP & No & 9 & -14.84 & 11.08 & 3.69\\
Performing & Dynamics & PtoF & No & 9 & 17.44 & 8.11 & 2.70\\
Teaching & Dynamics & PtoF & No & 9 & 20.66 & 12.09 & 4.03\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} N, SD and SEM represent sample size, standard deviation and standard error of the mean, respectively. Technique indicates performance data when participants playing the piece with either articulation (Fig.5 B) or dynamics (Fig.5 C). TeachingExp indicates if participants had an experience in teaching the piano.}
\end{tablenotes}

@@

A two-way repeated-measures ANOVA with the factors Condition (teaching vs.~performing) and Transition Type (FtoP vs.~PtoF) showed that there was a significant main effect of Transition Type (\emph{F}(1,19) = 42, \emph{p} \textless{} 0.001, \(\eta_G^2\) = 0.63). However, there was no significant interaction between Condition and Transition Type (\emph{F}(1,19) = 1.10, \emph{p} = 0.31, \(\eta_G^2\) = 0.008, \emph{Fig \ref{fig:vel-diff-2}}).
